Automated Formal Verification of Stand-alone Solar Photovoltaic Systems

### 2019-07-14 Tex/elsevier/reply Solar Energy JULY 2019.tex
revised comment (7)
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\begin{resposta} 
As explained at the first question, here the authors failed in explain better the study. We appreciate one more time the comment and the opportunity to correct this issue.

At the paper, we compare model checking with simulation tool. However how they work is completely different. Simulation depends on the choice of input variables (and their values) in order to obtain the output. In the other hand, model checking performs an automatic output search that causes the system to fails (a not expected behavior of the system) and presents the input that causes it. Therefore with model checking we can prove the absence of system flaws.

When we work with waveform we are performing testing of simulation, and that is different of automated verification that is a mathematical prove (of correctness or flaw). Based on the fact that the authors have the five cases deployed at the field, and with monitoring system in four those PV systems, it is possible to add waveforms to the work. However, the use of this resource seems that is not a adequate way of comparative. However, we included details about the estimated load curve of each case study at the revised paper (section 4) that is represented by a vector with 24 elements (one to each hour of the day).
\end{resposta}
\end{quote}

>>>>

\begin{resposta}

We agree with the reviewer that we could further improve the explanation of our study. In our manuscript, we compare model checking with software simulation. However, the way they work is completely different. On one hand, simulation depends on the choice of input variables (and their values) in order to obtain the output. On the other hand, model checking performs an exhaustive search with the goal of proving or violating a given property. In the latter case, if the property is violated (an unexpected behavior of the system), then a model checker presents the input that causes such a violation. Therefore, we can prove the absence of system flaws using model checking. This information was included in the revised version of our manuscript in Section X \textcolor{red}{could you please describe the section here?}.

When we work with waveform, we are performing testing of simulation \textcolor{red}{``testing of simulation'' sounds weird. Could you please explain it further here?}, and that is different of automated verification, which is a mathematical proof (of correctness or flaw). Based on the fact that the authors have the five cases deployed in field and with monitoring system in four those PV systems, it is possible to add waveforms to the work. However, the use of this resource seems that is not an adequate way of comparative \textcolor{red}{why not? could you please explain here?}. However, we included details about the estimated load curve of each case study in the revised version of our manuscript (cf. Section $4$), which is represented by a vector with $24$ elements (one to each hour of the day).
\end{resposta}
\end{quote}
